\documentclass[11pt]{article}
\usepackage[letterpaper, margin=2cm]{geometry}
\usepackage{titlesec}
\usepackage{mdframed}
\usepackage[dvipsnames]{xcolor} % for color names, must be loaded before tikz
\usepackage{ifthen}
\usepackage{comment}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{amsmath, amssymb, amsthm}

\providecommand{\due}{}
\lhead{Virtualization} \rhead{The University of Texas}
\lfoot{\due} \cfoot{} \rfoot{Page \thepage}
\renewcommand{\footrulewidth}{0.4pt}
\pagestyle{fancy}

% Eliminates the spacing in the title that remains from the empty author section.
\preauthor{}
\postauthor{}

\titleformat{\section}[runin]{\large\bfseries}{\thesection .}{3pt}{}
\titleformat{\subsection}[runin]{\bfseries}{\thesubsection)}{3pt}{}
\renewcommand\thesubsection{\alph{subsection}}

% Defines the solution environment. Toggle solutions between true and false to either show or hide solutions. Also, the solution environment takes an optional argument of arbitrary text to be inserted in the solution header.
\newboolean{solutions}
\setboolean{solutions}{true}
\ifthenelse{\boolean{solutions}}
{\newenvironment{solution}{\begin{mdframed}[skipbelow=0pt, linecolor=White, backgroundcolor=Green!10]\textbf{Solution:}}{\end{mdframed}}}
{\excludecomment{solution}}

\allowdisplaybreaks

\begin{document}

\title{Virtualization\\Pre-lab Questions --- \#3}
\date{\due}

\maketitle

\noindent \textbf{Point total:} 4
\\ All homework assignments are weighted equally in the final grade. Point values are unique to each lab assignment.

\textbf{Note:} For all problems which ask you to explain your reasoning or show your work, you do not need to show every step of each calculation, but the answer should include an explanation \emph{written with words} of what you did.  Even when work is not required to be shown, it’s a good idea to include anyways so that you can earn partial credit.

\section{Question [1 point]}

Name 3 different events that might cause a vmexit. You can look through some of the reasons in \texttt{vmm/vmx.c}, but it may be easier to reason this from your knowledge of operating systems and virtual machines

\begin{solution}
1. An external interruption (e.g. the host OS shuts down the hypervisor process or something like that.)

2. An I/O interruption might cause the VM to exit.

3. An exception, like an EPT violation could cause the VM to exit. 
\end{solution}


\section{Question [1 point]}

What overhead costs exist when you do a VM exit? Give an example in the codebase of one of these computation costs. Provide the function and file, and an explanation.

\begin{solution}
There are multiple overhead costs when performing a VM ext. Namely, context switching overhead, general resource management, handling the actual exit event, and then handling the return.
In our codebase we can see that in the handle_eptviolation() function in vmm/vmexits.c. In this function we have to perform a whole new EPT mapping, if this is performed frequently, the overhead 
could be quite large. 

\end{solution}


\section{Question [1 point]}

Recall that the \texttt{\%cr3} register holds the physical address of a page table. An OS kernel needs to change \texttt{\%cr3} during context switches to switch page tables. Does our VM, which has hardware supported page tables for virtual machines also have to do this? GDB does not display the \texttt{\%cr3} register, but you can check it using the QEMU monitor before and after a vmexit is issued.

\begin{solution}
Yes, we still have to switch the cr3 register when performing a context swith even with hardware supported pagetables. 
\end{solution}


\section{Question [1 point]}

In Part-3 of this project, you will be responsible for filling in pieces in the codebase to boot the VM. What is a bootloader? How do we ensure isolation between machines booting in memory?

\begin{solution}
A bootloader is just a program responsible for loading an OS into memory and starting it. We achieve isolation by pointing to different memory addresses for the different VMs. Furthermore, 
each VM has its own virtual address space which has a unique mapping to a physical address space. The hypervisor is responsible for doing this. 
\end{solution}


\end{document}
